---
title: "Bind Edges"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bind Eges}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
library(htmltools)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats", n = 1000, include_rts = FALSE, token = token, lang = "en")
```

Two core functions of graphTweets are `gt_edges` and `gt_co_edges` which come with sister functions: `gt_edges_bind` and `gt_co_edges_bind` that help bind edges together to build more complex graphs.

Let's get some tweets again.

```{r, eval = FALSE}
library(rtweet)

# 1'000 tweets on #rstats, excluding retweets
tweets <- search_tweets("#rstats filter:mentions", n = 500, include_rts = FALSE)
```

In other sections we detailed, amongst other things, how to build 1) a network of hashtags and 2) a network of users connected to the hashtags they use in their tweets: how about we bind these two?

```{r}
net <- tweets %>% 
  gt_co_edges(mentions_screen_name) %>%
  gt_edges_bind(screen_name, hashtags) %>%
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net

library(dplyr)

edges <- edges %>% 
  mutate(id = 1:n()) 

nodes <- nodes %>% 
  mutate(
    id = nodes,
    label = id,
    size = n
  )

library(sigmajs)

sigmajs() %>% 
  sg_nodes(nodes, id, label, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_cluster(
    colors = c(
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_layout(layout = igraph::layout_components) %>% 
  sg_neighbours() %>% 
  sg_settings(
    minNodeSize = 1,
    maxNodeSize = 3,
    defaultEdgeColor = "#a3a3a3",
    edgeColor = "default"
  )
```

_Functions are built in such a way to you can bind any edges together._