---
title: "Co-mentions"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Co-mentions}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats", n = 1000, include_rts = FALSE, token = token, lang = "en")
tweets_mentions <- search_tweets("#rstats  filter:mentions", n = 1000, token = token, lang = "en")
#tweets$text <- iconv(tweets$text, to = "UTF-8", sub = "")
```

graphTweets not only allows to build graphs of interactions between users. It also lets you visualise what hashtag users use in their tweets and which hashtags are used together in the same tweets.

## Hashtags Co-mentions

We can also build networks of hashtags co-mentions; when two or more hashtags are used in the same tweet they are connected on the graph.

Let's look at the hashtags associated with #rstats

```{r other tweets, message=FALSE, warning=FALSE}
tweets <- search_tweets("#rstats", n = 1000, include_rts = FALSE, token = token, lang = "en")
```

For this network use `gt_edges_hashes` and simply pass the `hashtags` column as it's all that is needed.

```{r}
net <- tweets %>% 
  gt_co_edges(hashtags) %>%
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net
```

Then again, we'll use `sigmajs` for the visualisation. Since we got tweets on `#rstats` we will remove this node, it will be connected to all other hashtags. _Make sure you remove it from both nodes and edges._

```{r}
library(dplyr)

edges <- edges %>% 
  mutate(
    id = 1:n()
  ) %>% 
  filter(source != "#rstats") %>% 
  filter(target != "#rstats")

nodes <- nodes %>% 
  mutate(
    id = nodes,
    label = id,
    size = n
  ) %>% 
  filter(id != "#rstats") %>% 
  select(id, label, size)

library(sigmajs)

sigmajs() %>% 
  sg_nodes(nodes, id, label, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_cluster(
    colors = c(
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_layout() %>% 
  sg_neighbours() %>% 
  sg_settings(
    defaultEdgeColor = "#a3a3a3",
    edgeColor = "default"
  )
```

## Users co-mentions

We can also build networks of co-mentions where users that are \@tagged in the same tweet are connected. We'll collect more tweets, with a slightly different queries to ensure that the tweets include \@mentions.

```{r other tweets 2, message=FALSE, warning=FALSE}
tweets_mentions <- search_tweets("rstats filter:mentions", n = 1000, token = token, lang = "en")
```

When preparing the graph we simply pass `mentions_screen_name` instead of `hashtags` as we did before.

```{r}
net <- tweets_mentions %>% 
  gt_co_edges(mentions_screen_name) %>%
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net

edges <- edges %>% 
  mutate(id = 1:n()) 

nodes <- nodes %>% 
  mutate(
    id = nodes,
    label = id,
    size = n
  )

sigmajs() %>% 
  sg_nodes(nodes, id, label, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_cluster(
    colors = c(
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_layout(layout = igraph::layout.fruchterman.reingold) %>% 
  sg_neighbours() %>% 
  sg_settings(
    maxNodeSize = 3,
    defaultEdgeColor = "#a3a3a3",
    edgeColor = "default"
  )
```
