---
title: "Dynamic Graphs"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dynamic Graphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats", n = 1000, include_rts = FALSE, token = token, lang = "en")
tweets$text <- iconv(tweets$text, to = "UTF-8", sub = "")
```

## What

What is a dynamic graph? A graph that includes an additional dimension which renders is dynamic. Here we'll create a temporal graph

## How

Start by making the graph, see "Get Started" vignette if you do not know how to get tweets.

```{r}
tweets %>% 
  gt_edges(text, screen_name, status_id, "created_at") %>% 
  gt_nodes() %>% 
  gt_dyn() %>% 
  gt_collect() -> net
```

A few things to note.

1. We pass `created_at` in `gt_edges` as we want to know the time at which the edge is created.
2. We get the nodes with `gt_nodes`
3. We use `gt_dyn` (short for "dynamic") to get the dynamic graph.

Let's look at the output.

```{r}
knitr::kable(head(net$edges))
```

The edges include the `created_at` column (date time when the tweet is posted).

```{r}
knitr::kable(head(net$nodes))
```

The nodes include `start` and `end` column, this is added by the `gt_dyn` function; which, in effect, simply computes when the node should appear on the graph.

I use [sigmajs](http://sigmajs.john-coene.com/) to visualise the dynamic graph, please see the website if you want to understand the code below, being a different package I do not get into this here. In brief, I convert date time to numeric and rescale edge appearances between 0 and 5000 milliseconds.

```{r}
library(sigmajs)

# convert to numeric & rescale
edges <- net$edges %>% 
  dplyr::mutate( 
    id = 1:n(),
    created_at = as.numeric(created_at),
    created_at = (created_at - min(created_at)) / (max(created_at) - min(created_at)),
    created_at = created_at * 5000
  )

nodes <- net$nodes %>% 
  dplyr::mutate(
    id = source,
    size = n_edges
  )

mx <- max(edges$created_at) + 500

sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, size) %>% 
  sg_add_edges(edges, created_at, id, source, target, cumsum = FALSE) %>% 
  sg_force_stop(delay = mx) %>% 
  sg_settings(defaultNodeColor = "#1967be")
```