---
title: "Dynamic Graphs"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dynamic Graphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
library(htmltools)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats", n = 1000, include_rts = FALSE, token = token, lang = "en")
```

## What

What is a dynamic graph? A graph that includes an additional dimension which renders is dynamic. Here we'll create a temporal graph

## How

Start by making the graph, see "Get Started" vignette if you do not know how to get tweets.

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name, created_at) %>% 
  gt_nodes() %>% 
  gt_dyn() %>% 
  gt_collect() -> net
```

A few things to note.

1. We pass `created_at` in `gt_edges` as we want to know the time at which the edge is created.
2. We get the nodes with `gt_nodes`
3. We use `gt_dyn` (short for "dynamic") to get the dynamic graph.

Let's look at the output.

```{r}
knitr::kable(head(net$edges))
```

The edges include the `created_at` column (date time when the tweet is posted).

```{r}
knitr::kable(head(net$nodes))
```

The nodes include `start` and `end` column, this is added by the `gt_dyn` function; which, in effect, simply computes when the node should appear on the graph.

I use [sigmajs](http://sigmajs.john-coene.com/) to visualise the dynamic graph, please see the website if you want to understand the code below, being a different package I do not get into this here. In brief, I convert date time to numeric and rescale edge appearances between 0 and 10 seconds (so that the animation lasts 10 seconds), I then add 5 seconds so that the animation starts after 5 seconds (to give you a chance to see it in action).

*Click the trigger to add the edges.*

```{r, warning=FALSE,message=FALSE}
library(sigmajs)

# convert to numeric & rescale
edges <- net$edges %>% 
  dplyr::mutate( 
    id = 1:dplyr::n(),
    created_at = as.numeric(created_at),
    created_at = (created_at - min(created_at)) / (max(created_at) - min(created_at)),
    created_at = created_at * 10000
  )

nodes <- net$nodes %>% 
  dplyr::mutate(
    id = nodes,
    label = nodes,
    size = n
  )

# graph layout 
nodes <- sg_get_layout(nodes, edges)

nodes <- sg_get_cluster(nodes, edges, colors = c("#2780e3", "#d3d3d3")) # cluster

sigmajs() %>% 
  sg_nodes(nodes, id, size, label, x, y, color) %>% 
  sg_add_edges(edges, created_at, id, source, target, 
               cumsum = FALSE, refresh = TRUE) %>% 
  sg_button("add_edges", tags$i(class = "fa fa-play"), class = "btn btn-primary") %>% 
  sg_settings(defaultNodeColor = "#1967be")
```

Note that you can also dynamically add nodes, much of it explained in the [twinetbook](https://twinetbook.john-coene.com/).

```{r, echo=FALSE}
tags$a(
  href = "https://twinetbook.john-coene.com/",
  target = "_blank",
  "Twinetbook"
)
```