---
title: "Get Started"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
library(dplyr)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats", n = 500, include_rts = FALSE, token = token, lang = "en")
#tweets$text <- iconv(tweets$text, to = "UTF-8", sub = "")
```

`graphTweets` 4.0 has been redisigned to work hand-in-hand with [`rtweet`](http://rtweet.info/). Let's start by getting some tweets. *If you're unsure how to get started, head over to the rtweet website, everything is very well explained.* We'll get 1,000 tweets on [#rstats](https://twitter.com/search?q=%23rstats), exluding re-tweets.

```{r, eval = FALSE}
library(rtweet)

# 1'000 tweets on #rstats, excluding retweets
tweets <- search_tweets("#rstats", n = 500, include_rts = FALSE)
```

Now we can start using `graphTweets`.

1. Get the edges using `gt_edges`.
2. Build an `igraph` object using `gt_graph` or collect results with `gt_collect`.

#### igraph

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_graph() -> graph

class(graph)
```

#### List

If you do not want to return an `igraph` object, use `gt_collect`, it will return a list of two data.frames; edges and nodes.

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_collect() -> edges

names(edges)
```

(It also returns `nodes` but it's empty since we only ran `gt_edges`).

So far we only used `gt_edges` to extract the edges, we can also extract the nodes.

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect() -> graph

lapply(graph, nrow) # number of edges and nodes
lapply(graph, names) # names of data.frames returned
```

On `graphTweets` version `0.4.1` `gt_nodes` returns the number of edges the node is present in: `n_edges`. *Here I used `gt_collect`, you can, again, use `gt_graph` if you want to return an `igraph` object.*

Adding nodes has not bring much to table however, `gt_nodes` takes another argument, `meta`, which if set to `TRUE` will return meta data on each node, where availbale\*. More information on passing meta data to nodes further down the document.

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph

# lapply(graph, names) # names of data.frames returned
```

Note that you can also pass meta-data to edges if needed.

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name, created_at) %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph
```

Before we plot out graph, we're going to modify some of the meta-data, a lot of `NA` are returned (where the meta-data was not available \*). 

Here I use [sigmajs](http://sigmajs.john-coene.com) to plot the graph.

```{r}
library(dplyr)
library(sigmajs) # for plots

tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect() -> gt

nodes <- gt$nodes %>% 
  mutate(
    id = nodes,
    label = nodes,
    size = n,
    color = "#1967be"
  ) 

edges <- gt$edges %>% 
  mutate(
    id = 1:n()
  )

sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000)
```

Let's look at communities, we'll return an `igraph` object with `gt_graph` so we can easily run a community finding algorithm from the `igraph` package.

```{r}
tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_graph() -> g

class(g)
```

## Users to Hashtags

```{r, eval=FALSE}
library(rtweet)
tweets <- search_tweets("#rstats OR #python", n = 1000, include_rts = FALSE, token = token, lang = "en")
```

The same principles follow, we simply use `gt_edges_hash` and pass the `hashtags` column as returned by rtweet. This creates a `tibble` of edges from `screen_name` to `hashtags` used in each tweet.

```{r}
net <- tweets %>% 
  gt_edges(screen_name, hashtags) %>% 
  gt_nodes() %>% 
  gt_collect()
```

We'll visualise the graph with [sigmajs](http://sigmajs.john-coene.com/). Let's prepare the data to meet the library's requirements.

* We add `id` to both nodes and edges
* We add rename a few columns to meet sigmajs' convention
* We color the nodes by `type` (hashtag or user)

_Apologies for not getting into details here but sigmajs is very well documented, check the [website](http://sigmajs.john-coene.com/) if you want to understand it all_.

```{r}
edges <- net$edges
nodes <- net$nodes

edges$id <- seq(1, nrow(edges))
nodes$id <- nodes$nodes
nodes$label <- nodes$nodes
nodes$size <- nodes$n
nodes$color <- ifelse(nodes$type == "user", "#0084b4", "#1dcaff")
```

Let's visualise it.

```{r, echo=FALSE}
library(sigmajs)

sigmajs() %>% 
  sg_nodes(nodes, id, size, color, label) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout(layout = igraph::layout_components) %>% 
  sg_settings(
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  ) %>% 
  sg_neighbours()
```

We use `sg_layout` to layout the graph and `sg_neightbours` to highlight nodes on click.

## Retweets

You can also build networks of retweets.

```{r}
tweets <- search_tweets("#rstats filter:retweets", n = 500, include_rts = TRUE, token = token, lang = "en")
```

```{r}
net <- tweets %>% 
  gt_edges(screen_name, retweet_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net

edges$id <- 1:nrow(edges)
edges$size <- edges$n

nodes$id <- nodes$nodes
nodes$label <- nodes$nodes
nodes$size <- nodes$n

sigmajs() %>% 
  sg_nodes(nodes, id, size, label) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout() %>% 
  sg_cluster(colors = c("#0C46A0FF", "#41A5F4FF")) %>% 
  sg_settings(
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  ) %>% 
  sg_neighbours()
```

## Retweets & Quotes

We can bind quoted tweets (surely they should be considered as retweets) using `gt_bind_edges`. 

```{r}
net <- tweets %>% 
  gt_edges(screen_name, retweet_screen_name) %>% 
	gt_edges_bind(screen_name, quoted_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net

edges$id <- 1:nrow(edges)
edges$size <- edges$n

nodes$id <- nodes$nodes
nodes$label <- nodes$nodes
nodes$size <- nodes$n

sigmajs() %>% 
  sg_nodes(nodes, id, size, label) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout() %>% 
  sg_cluster(colors = c("#0C46A0FF", "#41A5F4FF")) %>% 
  sg_settings(
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  ) %>% 
  sg_neighbours()
```

## Meta data

You can pass meta data to the edges and subsequently to the nodes using `gt_add_meta`.

```{r}
gt <- tweets %>% 
    gt_edges(screen_name, retweet_screen_name, followers_count, retweet_followers_count) %>% 
    gt_nodes() %>% 
    gt_add_meta(name = size, source = followers_count, target = retweet_followers_count)

# size is now number of followers
head(gt$nodes)

gt$edges$id <- 1:nrow(gt$edges)
gt$nodes$id <- gt$nodes$nodes
gt$nodes$label <- gt$nodes$nodes
gt$nodes$color <- scales::col_numeric(c("#41A5F4FF", "#0C46A0FF"), NULL)(gt$nodes$size)

sigmajs() %>% 
  sg_nodes(gt$nodes, id, size, label, color) %>% 
  sg_edges(gt$edges, id, source, target) %>% 
  sg_layout() %>% 
  sg_settings(
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  ) %>% 
  sg_neighbours()
```

\* Some nodes are mentioned in tweets only and therefore have no meta-data associated.