---
title: "Get Started"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(igraph)
library(dplyr)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats", n = 500, include_rts = FALSE, token = token, lang = "en")
#tweets$text <- iconv(tweets$text, to = "UTF-8", sub = "")
```

`graphTweets` 4.0 has been redisigned to work hand-in-hand with [`rtweet`](http://rtweet.info/). Let's start by getting some tweets. *If you're unsure how to get started, head over to the rtweet website, everything is very well explained.* We'll get 1,000 tweets on [#rstats](https://twitter.com/search?q=%23rstats), exluding re-tweets.

```{r, eval = FALSE}
library(rtweet)

# 1'000 tweets on #rstats, excluding retweets
tweets <- search_tweets("#rstats", n = 500, include_rts = FALSE)
```

Now we can start using `graphTweets`.

1. Get the edges using `gt_edges`.
2. Build an `igraph` object using `gt_graph` or collect results with `gt_collect`.

#### igraph

```{r}
tweets %>% 
  gt_edges(text, screen_name, status_id) %>% 
  gt_graph() -> graph

class(graph)
```

#### List

If you do not want to return an `igraph` object, use `gt_collect`, it will return a list of two data.frames; edges and nodes.

```{r}
tweets %>% 
  gt_edges(text, screen_name, status_id) %>% 
  gt_collect() -> edges

names(edges)
```

(It also returns `nodes` but it's empty since we only ran `gt_edges`).

So far we only used `gt_edges` to extract the edges, we can also extract the nodes.

```{r}
tweets %>% 
  gt_edges(text, screen_name, status_id) %>% 
  gt_nodes() %>% 
  gt_collect() -> graph

lapply(graph, nrow) # number of edges and nodes
lapply(graph, names) # names of data.frames returned
```

On `graphTweets` version `0.4.1` `gt_nodes` returns the number of edges the node is present in: `n_edges`. *Here I used `gt_collect`, you can, again, use `gt_graph` if you want to return an `igraph` object.*

Adding nodes has not bring much to table however, `gt_nodes` takes another argument, `meta`, which if set to `TRUE` will return meta data on each node, where availbale\*.

```{r}
tweets %>% 
  gt_edges(text, screen_name, status_id) %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph

# lapply(graph, names) # names of data.frames returned
```

Note that you can also pass meta-data to edges if needed.

```{r}
tweets %>% 
  gt_edges(text, screen_name, status_id, datetime = "created_at") %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph
```

Before we plot out graph, we're going to modify some of the meta-data, a lot of `NA` are returned (where the meta-data was not available \*). 

Here I use [sigmajs](http://sigmajs.john-coene.com) to plot the graph.

```{r}
library(dplyr)
library(sigmajs) # for plots

tweets %>% 
  gt_edges(text, screen_name, status_id, datetime = "created_at") %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> gt

nodes <- gt$nodes %>% 
  mutate(
    id = nodes,
    label = ifelse(is.na(name), nodes, name),
    size = n_edges,
    color = "#1967be"
  ) 

edges <- gt$edges %>% 
  mutate(
    id = 1:n()
  )

sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000)
```

Let's look at communities, we'll return an `igraph` object with `gt_graph` so we can easily run a community finding algorithm from the `igraph` package.

```{r}
library(igraph)

tweets %>% 
  gt_edges(text, screen_name, status_id) %>% 
  gt_graph() -> g

# communities
wc <- walktrap.community(g)
V(g)$color <- membership(wc)

# plot
# tons of arrguments because defaults are awful
plot(g, 
     layout = igraph::layout.fruchterman.reingold(g), 
     vertex.color = V(g)$color,
     vertex.label.family = "sans",
     vertex.label.color = hsv(h = 0, s = 0, v = 0, alpha = 0.0),
     vertex.size = igraph::degree(g), 
     edge.arrow.size = 0.2, 
     edge.arrow.width = 0.3, edge.width = 1,
     edge.color = hsv(h = 1, s = .59, v = .91, alpha = 0.7),
     vertex.frame.color="#fcfcfc")
```

\* Some nodes are mentioned in tweets only and therefore have no meta-data associated.