---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(graphTweets)
library(rtweet)
token <- readRDS("../twitter_token.rds")
tweets <- search_tweets("#rstats #python", n = 1000, include_rts = FALSE, token = token, lang = "en")
tweets$text <- iconv(tweets$text, to = "UTF-8", sub = "")
```

graphTweets not only allows to build graphs of interactions between users. It also lets you visualise what hashtag users use in their tweets.

```{r, eval=FALSE}
library(rtweet)
tweets <- search_tweets("#rstats #python", n = 1000, include_rts = FALSE, token = token, lang = "en")
```

The same principles follow, we simply use `gt_edges_hash` and pass the `hashtags` column as returned by rtweet. This creates a `tibble` of edges from `screen_name` to `hashtags` used in each tweet.

```{r}
net <- tweets %>% 
  gt_edges_hash(hashtags, screen_name) %>% 
  gt_nodes() %>% 
  gt_collect()
```

We'll visualise the graph with [sigmajs](http://sigmajs.john-coene.com/). Let's prepare the data to meet the library's requirements.

* We add `id` to both nodes and edges
* We add rename a few columns to meet sigmajs' convention
* We color the nodes by `type` (hashtag or user)

_Apologies for not getting into details here but sigmajs is very well documented, check the [website](http://sigmajs.john-coene.com/) if you want to understand it all_.

```{r}
edges <- net$edges
nodes <- net$nodes

edges$id <- seq(1, nrow(edges))
nodes$id <- nodes$nodes
nodes$label <- nodes$nodes
nodes$size <- nodes$n_edges
nodes$color <- ifelse(nodes$type == "user", "#0084b4", "#1dcaff")
```

Let's visualise it.

```{r}
library(sigmajs)

sigmajs() %>% 
  sg_nodes(nodes, id, size, color, label) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout(layout = igraph::layout_components) %>% 
  sg_settings(
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  ) %>% 
  sg_neighbours()
```

We use `sg_layout` to layout the graph and `sg_neightbours` to highlight nodes on click.